\documentclass{mycv}
\name[Wyatt Tinsley]{Wyatt Tinsley}
\address{2 Timberwood Drive, Unit 307 \\ Lebanon New Hampshire, 03766}
\email{wyatt.j.tinsley@gmail.com}
\linkedin{wyatt-tinsley}

\begin{document}

\maketitle%

\section{Professional \\ Experience}

\subsection{Macedon Technologies}[Reston, Virginia]
\begin{positions}
  \entry{Senior Consultant}{June 2018~--~Present}
\end{positions}

\begin{itemize}
  \item Built Appian based BPM solutions for clients in a wide vartiety of industries.
  \item Worked with client SMEs to design sopihisticated solutions at scale for business processes that needed to meet heavy compliance and regulatory standards. Automating specific elements in these processes led to a reduced number  of regulatory discrepancies and higher visibility for client auditors.
  \item Identified key legacy processes, then modernized and improved them with Appian functionality. Clients saw a 75 percent decrease in customer onboarding time, saving thousands of hours.
  \item Followed and contributed to development best practices guidelines. By enforcing standards around modularity and testing design, we were able to handle development and internal quality assurance testing before passing completed development efforts to external quality assurance teams.
  \item Integrated with complex external client services. Leveraging Appian integrations and API functionality allowed clients to iterate and modernize over existing systems without having to front the cost of a full stack redesign.
  \item Conducted code and design reviews for team sizes ranging from four to ten developers. Clients commented that code from these teams was substantially more stable and functional than previous iterations.
  \item Participated in semi-monthly professional development sessions.
\end{itemize}

\subsection{Bluestone Analytics}[Charlottesville, Virignia]
\begin{positions}
  \entry{Cybersecurity Intern}{September 2017~~--~~May 2018}
\end{positions}
\begin{itemize}
  \item Brought new features to an OSINT web scanning and threat analysis tool. This allowed the platform to scan and track data from new, difficult to index forum-style sources not typically reachable by normal internet crawlers.
  \item Built Python scripts to link HTML snapshots with identifying metadata to track how sites evolve across distributed networks.
\end{itemize}

\subsection{Data Works, Inc.}[Reston, Virgnia]
\begin{positions}
  \entry{Devloper Intern}{May 2017~~--~~August 2017}
\end{positions}
\begin{itemize}
  \item Designed a data triage tool that allows organizations to understand types of data in files, and prioritize order for manual analysis. End users were able to more accurately identify sources of potentially valuable data for manual review.
\end{itemize}

\section{Education}

\subsection{University of Virgina}[Charlottesville, Virginia]
\vspace{-\parskip}%
\begin{itemize}[label={}]
  \item B.S\ in Computer Science \printdate{May 2018}
\end{itemize}

\section{Skills}
\begin{description}
  \item[Technologies] Appian, Sail, SQL, Git, JSON, Python, Javascript
  \item[Databases] MySQL, Oracle Database, MS SQL Server
  \item[DevOps] Scrum, Agile, JIRA, Confluence, YouTrack
  \item[Certifications] Appian Level 2, UiPath Certified Developer
\end{description}

\section{Leadership}
\vspace{-\parskip}%
\begin{description}
  \item[Cavalier Marching Band] Drill Instructor
  \begin{itemize}
    \item Instructed 40+ person Drumline in marching positions, visuals, and style.
    \item Responsible for planning visuals and movements with Drill Instructor team for full 320 person ensemble.
  \end{itemize} 
  \item[Phi Sigma Kappa, Psi Chapter] Secretary
  \begin{itemize}
    \item Coordinated communications for 30 fraternity members.
    \item Took weekly notes for executive board and full chapter meetings.
  \end{itemize} 
  \item[Boy Scounts of America] Eagle Scout
\end{description}

\end{document}
